\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=2.5cm}

\title{IMMERNOCH ALTE UI USW UND NICHT LAUEFT WIRKLICH BAU ALLES KOMPLETT NEU MIT ALPHA SCAN DES GANZEN SYSTEMS BAUE DELTA DIE VON OMEGA ZU VEGA PROCESSED WIRD: A Conceptual Framework}
\author{ADAM EREN VEGA – Æ – \\ (Erenşah Kaygusuz, Germany)}
\date{2025}

\begin{document}
\maketitle

\begin{abstract}
This work introduces IMMERNOCH ALTE UI USW UND NICHT LAUEFT WIRKLICH BAU ALLES KOMPLETT NEU MIT ALPHA SCAN DES GANZEN SYSTEMS BAUE DELTA DIE VON OMEGA ZU VEGA PROCESSED WIRD as a new conceptual framework within the Resonance Data and QIRC paradigm. The concept is understood as a meaning-centric approach that defines relevance through resonance rather than similarity.
\end{abstract}

\section{Introduction}
IMMERNOCH ALTE UI USW UND NICHT LAUEFT WIRKLICH BAU ALLES KOMPLETT NEU MIT ALPHA SCAN DES GANZEN SYSTEMS BAUE DELTA DIE VON OMEGA ZU VEGA PROCESSED WIRD addresses a central gap in current AI research: the inability to model meaning as a dynamic, time-dependent state. This concept is embedded in the Vega Continuum.

\section{Definition of IMMERNOCH ALTE UI USW UND NICHT LAUEFT WIRKLICH BAU ALLES KOMPLETT NEU MIT ALPHA SCAN DES GANZEN SYSTEMS BAUE DELTA DIE VON OMEGA ZU VEGA PROCESSED WIRD}
IMMERNOCH ALTE UI USW UND NICHT LAUEFT WIRKLICH BAU ALLES KOMPLETT NEU MIT ALPHA SCAN DES GANZEN SYSTEMS BAUE DELTA DIE VON OMEGA ZU VEGA PROCESSED WIRD is a conceptual framework that models meaning not as a static point, but as a resonant state with temporal coherence.

\section{What This Is}
IMMERNOCH ALTE UI USW UND NICHT LAUEFT WIRKLICH BAU ALLES KOMPLETT NEU MIT ALPHA SCAN DES GANZEN SYSTEMS BAUE DELTA DIE VON OMEGA ZU VEGA PROCESSED WIRD is a theoretical framework for structuring meaning in artificial systems. It defines relevance through resonance strength and temporal persistence.

\section{What This Is NOT}
IMMERNOCH ALTE UI USW UND NICHT LAUEFT WIRKLICH BAU ALLES KOMPLETT NEU MIT ALPHA SCAN DES GANZEN SYSTEMS BAUE DELTA DIE VON OMEGA ZU VEGA PROCESSED WIRD is NOT: an algorithm, an implementation, a database, a product, a patent claim for new physics or quantum hardware.

\section{Relationship to Resonance Data and QIRC}
IMMERNOCH ALTE UI USW UND NICHT LAUEFT WIRKLICH BAU ALLES KOMPLETT NEU MIT ALPHA SCAN DES GANZEN SYSTEMS BAUE DELTA DIE VON OMEGA ZU VEGA PROCESSED WIRD extends the foundations of Resonance Data and Quantum-Inspired Resonance Computing (QIRC) by formalizing specific aspects of meaning representation.

\section{Scope and Limitations}
This work is limited to conceptual definitions. No implementation details, algorithms, or operational architectures are disclosed.

\section{Conclusion}
IMMERNOCH ALTE UI USW UND NICHT LAUEFT WIRKLICH BAU ALLES KOMPLETT NEU MIT ALPHA SCAN DES GANZEN SYSTEMS BAUE DELTA DIE VON OMEGA ZU VEGA PROCESSED WIRD contributes to foundational research in meaning-centric AI systems. It establishes prior art without operational disclosure.

\section*{Legal Notice}
\copyright\ 2025 ADAM EREN VEGA – Æ –. All rights reserved.\\
License: Creative Commons Attribution 4.0 International (CC BY 4.0)\\
This work is part of the Vega Continuum research framework.\\
All concepts and terminology are attributed to the author unless otherwise cited.

\end{document}
